### 2015-11-30 fundamentals/impl.tex
adds examples of resource computing as a parenthetical. Indeed, we did mean cloud and cluster computing

Innovative approaches to designing and optimizing robust fuel cycle strategies can become available by leveraging modern parallel computing resources.  For example, large scale sensitivity analyses to quantify the dependence of fuel cycle outcomes on potentially hundreds of uncertain parameters would only be feasible in a massively parallelized environment.
However, many fuel cycle simulators rely on \gls{COTS} and Windows-only software that limits
performance on and compatibility with resource computing infrastructures. This
constrains the possible scope of simulations and increases the wall-clock time necessary to conduct parameterized sensitivity
analyses and other multi-simulation studies. \Cyclus, on the other hand, is
primarily written in \texttt{C++} and relies on
libraries supported by Linux and UNIX (including Ubuntu and OSX) platforms,
which are flexible and support parallelization.
Furthermore, the core infrastructure and related archetypes are free and
open source, BSD-3-clause licensed.  \Cyclus can therefore be easily deployed
on large computer systems, such as \gls{HTC} systems.

>>>>

Innovative approaches to designing and optimizing robust fuel cycle strategies can become available by leveraging modern parallel computing resources.  For example, large scale sensitivity analyses to quantify the dependence of fuel cycle outcomes on potentially hundreds of uncertain parameters would only be feasible in a massively parallelized environment.
However, many fuel cycle simulators rely on \gls{COTS} and Windows-only software that limits
performance on and compatibility with resource computing infrastructures (e.g. 
cluster or cloud computing). This
constrains the possible scope of simulations and increases the wall-clock time necessary to conduct parameterized sensitivity
analyses and other multi-simulation studies. \Cyclus, on the other hand, is
primarily written in \texttt{C++} and relies on
libraries supported by Linux and UNIX (including Ubuntu and OSX) platforms,
which are flexible and support parallelization.
Furthermore, the core infrastructure and related archetypes are free and
open source, BSD-3-clause licensed.  \Cyclus can therefore be easily deployed
on large computer systems, such as \gls{HTC} systems.
